---
output:
  html_document:
    css: "style.css"
    toc: false
    toc_depth: 2
    toc_float:
    collapsed: false
    theme: flatly
    fig_width: 10 
    fig_height: 7 
params:
    main_config: NULL
    prevalence_time_series: NULL
    previous_prevalence_time_series: NULL
    reference_day_vs_weeks_before_probabilities: NULL
    country_configs: NULL
    cleaned_aggregated_sample: NULL
    aggregated_HH: NULL
    aggregated_sample: NULL
    post_stratified_draws: NULL
    
title: "Prevalence of Infections by Region, Country and Variant"
subtitle: "Quality report"
date: "`r format(Sys.time(), '%d %B %Y')`"
author:
    name: Covid Infection Survey Analysis Team
---

```{r ons-logo, echo=FALSE}
htmltools::img(src = gcptools::ons_logo(), 
               alt = 'logo', 
               style = 'position:absolute; top:0; padding:10px; padding-bottom:40px; width:352px; height:160px')
```
<div>
<font color ="red">
<b>OFFICIAL SENSITIVE</b><br />
DO NOT SHARE WITHOUT PERMISSION
<font color ="black">
</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      echo = FALSE)
                      
library(dplyr)
library(kableExtra)
library(magrittr)

main_config <- params$main_config
prevalence_time_series <- params$prevalence_time_series
reference_day_vs_weeks_before_probabilities <- params$reference_day_vs_weeks_before_probabilities
country_configs <- params$country_configs
cleaned_aggregated_sample <- params$cleaned_aggregated_sample
pos_by_day <- params$pos_by_day
post_stratified_draws <- params$post_stratified_draws
posterior_draws <- params$posterior_draws

```

**Data run on:** `r format(as.Date(main_config$run_settings$data_run, "%Y%m%d"), "%d %B %Y")`<br />
**Previous run on:** `r format(as.Date(main_config$run_settings$prev_data_run, "%Y%m%d"), "%d %B %Y")`<br />

# Results {.tabset .tabset-pills}

## England {.tabset .tabset-pills}

**Includes data up to:** `r format(main_config$run_settings$end_date[["England"]],"%d %B %Y")`<br /> 
**Reference day:** `r format(main_config$run_settings$end_date[["England"]] - 3, "%d %B %Y")` 

```{r fortnightly-trend-summary-england}

create_coloured_trends_table(reference_day_vs_weeks_before_probabilities, 
                             "England", 
                             "ctall", 
                             "country")

```
-  `r get_summary_statement(current_vs_previous_probabilities, "England", "ctall")`
-  `r get_population_numbers_statement(filtered_pop_tables, prevalence_time_series, "England", "ctall")`
-  `r get_population_percentage_statement(prevalence_time_series,"England", "ctall")`
- `r get_previous_population_percentage_statement(previous_prevalence_time_series,"England", "ctall")`
- Caution should be taken in over-interpretting any small movements in the latest trends

### Comparison with previously published

```{r overlay-plot-england}
create_overlay_plot(prevalence_time_series, 
                    previous_prevalence_time_series, 
                    "England", 
                    "ctall",
                    "country")
```

### Spaghetti Plot

```{r spaghetti-plot-england}

spaghetti_plot(prevalence_time_series, 
               post_stratified_draws, 
               "England", 
               "ctall", 
               "country", 
               main_config)

```

### By Variant

```{r overlay-variant-breakdown-england}

create_variant_overlay(prevalence_time_series, 
                       "England", 
                       main_config, 
                       "country")

```

### Comparison Against Raw

```{r raw-vs-modelled-england}

plot_raw_vs_modelled(sample_data = aggregated_sample,
                     household_data = aggregated_HH,
                     prevalence_time_series = prevalence_time_series,
                     COUNTRY =  "England",
                     country_configs = country_configs,
                     region_or_country = "country")  
```

### Low Returns

**How to interpret this plot:** 

- This plot shows the unweighted positivity or prevalence of infections (black) against an measure of daily returns. 
- This measure is calculated by taking the average number of returns per day over the period, and comparing each day to the period average. 
- Green bars indicate above average returns, whereas orange and red indicate below average returns. 
- When looking at the day to day changes in the unweighted prevalence, if there are a number of below average returns around that day, the estimates on that day may be less robust. 

``` {r low-returns-england}
data <- create_raw_counts_with_prevalence(aggregated_sample,
                                  aggregated_HH,
                                  prevalence_time_series)%>%
    dplyr::mutate(visit_date = lubridate::ymd(visit_date))%>%
    dplyr::filter(region == "England")%>%
    dplyr::group_by(region)%>%
    dplyr::mutate(average_n_returns = round(sum(N) / length(N),0),
                  n_over_average = N / average_n_returns * 100, 
                  diff_from_100 = n_over_average - 100,
                 "Unweighted Percentage" = (proportion*10))


 ggplot2::ggplot(data)+
     ggplot2::geom_col(ggplot2::aes(x = visit_date,
                                    y = -diff_from_100,
                                    fill = diff_from_100))+
     ggplot2::geom_point(ggplot2::aes(x = visit_date,
                                     y = `Unweighted Percentage`),
                                     size = 1)+
     ggplot2::geom_hline(ggplot2::aes(yintercept = 0),colour = "red", size = 2)+
     ggplot2::scale_y_continuous(name ="(Bars)\n% Daily Returns Below Average",
                                 breaks = seq(0,50,10), labels = c("Average","10%", 
                                                                     "20%","30%", "40%",
                                                                     "50%\nBelow\nAverage"),
                      sec.axis = ggplot2::sec_axis(~(./10), name = "(Black points)\nRaw Percentage",
                                                   labels = c("0%","1%","2%","3%", "4%", "5%")))+
    ggplot2::scale_x_date(date_breaks = "week", date_labels = "%d %b\n%Y")+
    ggplot2::coord_cartesian(ylim = c(-0,50))+
    ggplot2::scale_fill_stepsn(colours=c("darkred","yellow","darkgreen"), 
                               name = "% Returns\nCompared to\nAverage",
                               breaks=c(-200,-50,0))+
    theme_CIS()+
    ggplot2::labs(x = "Date")
```

### Raw vs Modelled Table

```{r positive-swabs-by-day-england}

create_raw_vs_prevalence_table(aggregated_sample,
                               aggregated_HH,
                               prevalence_time_series, 
                               "England",
                               "country")
```

### Configuration

```{r check-missing-dates-england, comment=NA}

check_missing_dates(cleaned_aggregated_sample, 
                    main_config)

```

**Model run in:** `r format(main_config$run_settings$environment)`<br />

```{r model-time-period-england}

start_date <- (main_config$run_settings$end_date$England) - (country_configs$England$run_settings$n_days_to_model)

end_date <- main_config$run_settings$end_date$England

model_time_period <- paste0(start_date, " - ", end_date)

```

**Model time period:** `r format(model_time_period)`<br />

**Variants run:** `r format(paste0(country_configs$England$run_settings$variants))`<br />

**Adapt Delta:** `r format(paste0(country_configs$England$model_settings$adapt_delta))`<br />

**Iterations:** `r format(paste0(country_configs$England$model_settings$iterations))`<br />

**Model formula:** `r format(get_model_formula(model = models, country = "England", variant = "1"))`<br />

**Divergent Transistions**

```{r divergent-table-england}

make_divergent_table(country_configs, "England", models, main_config)

```


## England Regions {.tabset .tabset-pills}


```{r fortnightly-trend-summary-england-regions}

create_coloured_trends_table(reference_day_vs_weeks_before_probabilities, 
                             "England", 
                             "ctall", 
                             "region")

```

### Comparison with previously published

```{r overlay-plot-england-regions}
create_overlay_plot(prevalence_time_series, 
                    previous_prevalence_time_series, 
                    "England", 
                    "ctall",
                    "region")
```

### Spaghetti Plot

```{r spaghetti-plot-england-regions}

spaghetti_plot(prevalence_time_series, 
               post_stratified_draws, 
               "England", 
               "ctall", 
               "region", 
               main_config)

```

### By Variant

```{r overlay-variant-breakdown-england-regions}

create_variant_overlay(prevalence_time_series, 
                       "England", 
                       main_config, 
                       "region")

```

### Comparison Against Raw

```{r raw-vs-modelled-england-regions}

plot_raw_vs_modelled(sample_data = aggregated_sample,
                     household_data = aggregated_HH,
                     prevalence_time_series = prevalence_time_series,
                     COUNTRY =  "England",
                     country_configs = country_configs,
                     region_or_country = "region")  
```

### Low Returns

``` {r low-returns-england-regions}

```

### Raw vs Modelled Table

```{r positive-swabs-by-day-england-regions}

create_raw_vs_prevalence_table(aggregated_sample,
                               aggregated_HH,
                               prevalence_time_series, 
                               "England",
                               "region")
```

### Configuration

```{r check-missing-dates-england-regions, comment=NA}

check_missing_dates(cleaned_aggregated_sample, 
                    main_config)

```

**Model run in:** `r format(main_config$run_settings$environment)`<br />

```{r model-time-period-england-regions}

start_date <- (main_config$run_settings$end_date$England) - (country_configs$England$run_settings$n_days_to_model)

end_date <- main_config$run_settings$end_date$England

model_time_period <- paste0(start_date, " - ", end_date)

```

**Model time period:** `r format(model_time_period)`<br />

**Variants run:** `r format(paste0(country_configs$England$run_settings$variants))`<br />

**Adapt Delta:** `r format(paste0(country_configs$England$model_settings$adapt_delta))`<br />

**Iterations:** `r format(paste0(country_configs$England$model_settings$iterations))`<br />

**Model formula:** `r format(get_model_formula(model = models, country = "England", variant = "1"))`<br />

**Divergent Transistions**

```{r divergent-table-england-regions}

make_divergent_table(country_configs, "England", models, main_config)

```

## Scotland {.tabset .tabset-pills}

```{r fortnightly-trend-summary-scotland}

create_coloured_trends_table(reference_day_vs_weeks_before_probabilities, 
                             "Scotland", 
                             "ctall", 
                             "country")

```
-  `r get_summary_statement(current_vs_previous_probabilities, "Scotland", "ctall")`
-  `r get_population_numbers_statement(filtered_pop_tables, prevalence_time_series, "Scotland", "ctall")`
-  `r get_population_percentage_statement(prevalence_time_series,"Scotland", "ctall")`
- `r get_previous_population_percentage_statement(previous_prevalence_time_series,"Scotland", "ctall")`
- Caution should be taken in over-interpretting any small movements in the latest trends


### Comparison with previously published

```{r overlay-plot-scotland}
create_overlay_plot(prevalence_time_series, 
                    previous_prevalence_time_series, 
                    "Scotland", 
                    "ctall",
                    "country")
```

### Spaghetti Plot

```{r spaghetti-plot-scotland}

spaghetti_plot(prevalence_time_series, 
               post_stratified_draws, 
               "Scotland", 
               "ctall", 
               "country", 
               main_config)

```

### By Variant

```{r overlay-variant-breakdown-scotland}

create_variant_overlay(prevalence_time_series, 
                       "Scotland", 
                       main_config, 
                       "country")

```

### Comparison Against Raw

```{r raw-vs-modelled-scotland}

plot_raw_vs_modelled(sample_data = aggregated_sample,
                     household_data = aggregated_HH,
                     prevalence_time_series = prevalence_time_series,
                     COUNTRY =  "Scotland",
                     country_configs = country_configs,
                     region_or_country = "country")  
```

### Low Returns

``` {r low-returns-scotland}

```

### Raw vs Modelled Table

```{r positive-swabs-by-day-scotland}

create_raw_vs_prevalence_table(aggregated_sample,
                               aggregated_HH,
                               prevalence_time_series, 
                               "Scotland",
                               "country")
```

### Configuration

```{r check-missing-dates-scotland, comment=NA}

check_missing_dates(cleaned_aggregated_sample, 
                    main_config)

```

**Model run in:** `r format(main_config$run_settings$environment)`<br />

```{r model-time-period-scotland}

start_date <- (main_config$run_settings$end_date$Scotland) - (country_configs$Scotland$run_settings$n_days_to_model)

end_date <- main_config$run_settings$end_date$Scotland

model_time_period <- paste0(start_date, " - ", end_date)

```

**Model time period:** `r format(model_time_period)`<br />

**Variants run:** `r format(paste0(country_configs$Scotland$run_settings$variants))`<br />

**Adapt Delta:** `r format(paste0(country_configs$Scotland$model_settings$adapt_delta))`<br />

**Iterations:** `r format(paste0(country_configs$Scotland$model_settings$iterations))`<br />

**Model formula:** `r format(get_model_formula(model = models, country = "Scotland", variant = "1"))`<br />

**Divergent Transistions**

```{r divergent-table-scotland}

make_divergent_table(country_configs, "Scotland", models, main_config)

```

## Wales {.tabset .tabset-pills}

```{r fortnightly-trend-summary-wales}

create_coloured_trends_table(reference_day_vs_weeks_before_probabilities, 
                             "Wales", 
                             "ctall", 
                             "country")

```

-  `r get_summary_statement(current_vs_previous_probabilities, "Wales", "ctall")`
-  `r get_population_numbers_statement(filtered_pop_tables, prevalence_time_series, "Wales", "ctall")`
-  `r get_population_percentage_statement(prevalence_time_series,"Wales", "ctall")`
- `r get_previous_population_percentage_statement(previous_prevalence_time_series,"Wales", "ctall")`
- Caution should be taken in over-interpretting any small movements in the latest trends

### Comparison with previously published

```{r overlay-plot-wales}
create_overlay_plot(prevalence_time_series, 
                    previous_prevalence_time_series, 
                    "Wales", 
                    "ctall",
                    "country")
```

### Spaghetti Plot

```{r spaghetti-plot-wales}

spaghetti_plot(prevalence_time_series, 
               post_stratified_draws, 
               "Wales", 
               "ctall", 
               "country", 
               main_config)

```

### By Variant

```{r overlay-variant-breakdown-wales}

create_variant_overlay(prevalence_time_series, 
                       "Wales", 
                       main_config, 
                       "country")

```

### Comparison Against Raw

```{r raw-vs-modelled-wales}

plot_raw_vs_modelled(sample_data = aggregated_sample,
                     household_data = aggregated_HH,
                     prevalence_time_series = prevalence_time_series,
                     COUNTRY =  "Wales",
                     country_configs = country_configs,
                     region_or_country = "country")  
```

### Low Returns

``` {r low-returns-wales}

```

### Raw vs Modelled Table

```{r positive-swabs-by-day-wales}

create_raw_vs_prevalence_table(aggregated_sample,
                               aggregated_HH,
                               prevalence_time_series, 
                               "Wales",
                               "country")
```

### Configuration

```{r check-missing-dates-wales, comment=NA}

check_missing_dates(cleaned_aggregated_sample, 
                    main_config)

```

**Model run in:** `r format(main_config$run_settings$environment)`<br />

```{r model-time-period-wales}

start_date <- (main_config$run_settings$end_date$Wales) - (country_configs$Wales$run_settings$n_days_to_model)

end_date <- main_config$run_settings$end_date$Wales

model_time_period <- paste0(start_date, " - ", end_date)

```

**Model time period:** `r format(model_time_period)`<br />

**Variants run:** `r format(paste0(country_configs$Wales$run_settings$variants))`<br />

**Adapt Delta:** `r format(paste0(country_configs$Wales$model_settings$adapt_delta))`<br />

**Iterations:** `r format(paste0(country_configs$Wales$model_settings$iterations))`<br />

**Model formula:** `r format(get_model_formula(model = models, country = "Wales", variant = "1"))`<br />

**Divergent Transistions**

```{r divergent-table-wales}

make_divergent_table(country_configs, "Wales", models, main_config)

```

## Northern Ireland {.tabset .tabset-pills}

```{r fortnightly-trend-summary-northern-ireland}

create_coloured_trends_table(reference_day_vs_weeks_before_probabilities, 
                             "Northern Ireland", 
                             "ctall", 
                             "country")

```

-  `r get_summary_statement(current_vs_previous_probabilities, "Northern Ireland", "ctall")`
-  `r get_population_numbers_statement(filtered_pop_tables, prevalence_time_series, "Northern Ireland", "ctall")`
-  `r get_population_percentage_statement(prevalence_time_series, "Northern Ireland", "ctall")`
- `r get_previous_population_percentage_statement(previous_prevalence_time_series, "Northern Ireland", "ctall")`
- Caution should be taken in over-interpretting any small movements in the latest trends


### Comparison with previously published

```{r overlay-plot-northern-ireland}
create_overlay_plot(prevalence_time_series, 
                    previous_prevalence_time_series, 
                    "Northern Ireland", 
                    "ctall",
                    "country")
```

### Spaghetti Plot

```{r spaghetti-plot-northern-ireland}

spaghetti_plot(prevalence_time_series, 
               post_stratified_draws, 
               "Northern Ireland", 
               "ctall", 
               "country", 
               main_config)

```

### By Variant

```{r overlay-variant-breakdown-northern-ireland}

create_variant_overlay(prevalence_time_series, 
                       "Northern Ireland", 
                       main_config, 
                       "country")

```

### Comparison Against Raw

```{r raw-vs-modelled-northern-ireland}

plot_raw_vs_modelled(sample_data = aggregated_sample,
                     household_data = aggregated_HH,
                     prevalence_time_series = prevalence_time_series,
                     COUNTRY =  "Northern Ireland",
                     country_configs = country_configs,
                     region_or_country = "country")  
```

### Low Returns

``` {r low-returns-northern-ireland}

```

### Raw vs Modelled Table

```{r positive-swabs-by-day-northern-ireland}

create_raw_vs_prevalence_table(aggregated_sample,
                               aggregated_HH,
                               prevalence_time_series, 
                               "Northern Ireland",
                               "country")
```

### Configuration

```{r check-missing-dates-northern-ireland, comment=NA}

check_missing_dates(cleaned_aggregated_sample, 
                    main_config)

```

**Model run in:** `r format(main_config$run_settings$environment)`<br />

```{r model-time-period-northern-ireland}

start_date <- (main_config$run_settings$end_date$`Northern Ireland`) - (country_configs$`Northern Ireland`$run_settings$n_days_to_model)

end_date <- main_config$run_settings$end_date$`Northern Ireland`

model_time_period <- paste0(start_date, " - ", end_date)

```

**Model time period:** `r format(model_time_period)`<br />

**Variants run:** `r format(paste0(country_configs$'Northern Ireland'$run_settings$variants))`<br />

**Adapt Delta:** `r format(paste0(country_configs$'Northern Ireland'$model_settings$adapt_delta))`<br />

**Iterations:** `r format(paste0(country_configs$'Northern Ireland'$model_settings$iterations))`<br />

**Model formula:** `r format(get_model_formula(model = models, country = "Northern Ireland", variant = "1"))`<br />

**Divergent Transistions**

```{r divergent-table-northern-ireland}

make_divergent_table(country_configs, "Northern Ireland", models, main_config)

```
